The rapid growth of different data sources, which produce large volumes of data in
real-time, makes choosing the best suitable technology stack and framework necessary.
For this reason, this research’s use case aims to find the best stateful stream processing framework that
can process petabytes of data in real-time and restore a state in case of fault tolerance.
State recovery in meaningful time is a crucial characteristic of stateful streaming systems
for this research.

\hspace{2em}The research focuses on two real-time streaming frameworks: Kafka
Streams and Apache Flink. These framework's community, open-source code, features,
and documentation have made them perfect for use in production environments for years.
During the research, will be built two prototypes with Kafka Streams and Apache Flink
that use the same input and output. The same input and output as Kafka topic is an efficient
point to get performance benchmarks for further analysis of two prototypes. Performance
benchmarks should show how the system behaves if all workers or some workers are down
for a short period.
This research is based on AWS and Kubernetes, which provide cloud infrastructure and
tools for running prototypes under stress. AWS is also a popular cloud provider for systems
that run in production environments.

\hspace{2em}The results should provide a useful benchmarks of Kafka Streams and Apache Flink frameworks that were
stressed in a production-like environment.
For this case study a
Chaos Mesh was chosen for a chaos simulation and reducing worker replicas during execution of experiments.
Collected benchmarks like CPU consumption, network utilization, and time for a state recoverу give an understanding
about what framework to choose.


%Software engineering is a diverse field that focuses on addressing various business domain problems.
%These domain-specific issues and their corresponding use cases necessitate in-depth analysis to determine
%the most suitable technologies for achieving optimal problem-solving outcomes.
%One rapidly growing area in software engineering is big data.
%Although big data is sometimes regarded as a marketing term, it encompasses complex data processing frameworks and datasets.
%
%As the volume of produced data has dramatically increased over the years,
%modern technical solutions capable of processing massive amounts of data are required.
%The open-source community offers a decent frameworks and tools, making it challenging to choose the best option.
%This research focuses on comparing the most suitable frameworks for specific use cases,
%particularly those that designed for stateful real-time stream processing.
%
%Stream processing use cases are relatively rare compared to typical problems that can often
%be solved with traditional batch processing or simple program which doesn't require MapReduce
%model or DAG.
%However, stateful stream processing assumes that real-time processing relies on previous states,
%and unbounded data flow which may indicate abnormal system behavior, such as fraud alerts in financial transactions
%within a specific time frame.
%Quick response can facilitate necessary actions and save time.
%Therefore, it is crucial to provide a technical analysis of the most suitable frameworks,
%assess their advantages and disadvantages, and examine the complexities involved in their
%application for stateful stream processing based on given use case.
%This master's thesis offers a technical overview,
%benchmarks, and comparisons for appropriate use cases.
%The use case examines considers that each incoming event triggers state re-computation and
%evaluates how efficiently Kafka Streams and Apache Flink manage state under heavy loads,
%represented by a stream of Kafka messages.
%The ideal framework should address existing problems while offering excellent scalability,
%fault tolerance, and cost efficiency.
%This master's thesis aims to provide an answer and a technical overview based on the given requirements.